%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%
% 2014-02-28 repurposed and tweaked by Josh Gardner for my own personal resume
% this is a new style and slight departure from previous resumes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Joshua}{Gardner}{A senior IT Infrastructure professional with 14 years experience} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Apt 8 - 2165 Oxford St.
Vancouver, BC V5L1E8
Canada
~
(604) 307 4801
~
josh.gardner@gmail.com
\section{os and tools}
Most Windows flavours
Linux and *nix-alikes
OpenBSD, Solaris
Puppet, Ansible, Salt
\section{virtualization}
VMWare 3.x, 4.x, 5.x
RHEV
\section{storage}
FC and iSCSI SAN
EMC Celerra
Hitachi HUS
Quantum Dxi
De-dupe
\section{mail}
Postfix, SpamAssasin
Policyd-weight, amavisd
Exim, Sendmail, QMail
\section{programming}
perl, PHP, LISP
C, C++, Java, bash
CSS \& HTML
\section{networking}
Cisco, HP ProCurve
WAN, MPLS
VPN, isakmpd
WAAS, BlueCoat
\section{database}
Oracle, MySql
PostgreSQL
SQL Server
\end{aside}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2013--Now}
{BUCKLAND \& TAYLOR}
{North Vancouver, British Columbia}
{\emph{North America Regional IT Manager} \\
Responsible for the development and delivery of IT projects for 4 companies and 400+ users across NA. Manages 3 direct reports across NA. Ensures that excellent solutions are delivered under-budget. Projects include: \\
\begin{itemize}
\item Project management of region-wide Windows upgrade, delivered on-time
\item Change management for a region-wide telephony replacement with Lync
\item Coordination of facility cabling upgrades, NA regional wifi rollout
\item Disaster recovery and business continuity planning and execution
\item Created new service desk in NA region, using ITIL and ITSM practices
\item Integration of newly-purchased entity into NA regional IT fabric
\item IT Policy governance for four organizations over \$10M monthly revenue
\item Budget responsibility for IT spend and organization SLA costs
\end{itemize}}
\\
%------------------------------------------------
\entry
{2008--2013}
{SYSCON JUSTICE SYSTEMS}
{Richmond, British Columbia}
{\emph{IT Manager} \\
Management responsibility for the worldwide IT department and team members, and all IT functions. \\
\begin{itemize}
\item Implemented IT best practices
\item Infrastructure, strategy, poliocy to enable annual 500\% revenue growth
\item Converted to 100\% virtualized servers, saved 1 FTE, 99.95\% uptime
\item Renegotiated telephony contracts, saved \$60K per year
\item Implemented a global service desk
\item Relocated head office (140 staff) with zero downtime
\item Deployed Cisco VOIP system, saved \$10K per year
\item Integration with software development and contuous release operation
\item Implemented automation, saved 1 FTE
\end{itemize}}
\\
%------------------------------------------------
\entry
{2007-2008}
{BRIGHTON CONSULTING}
{Vancouver, British Columbia}
{\emph{IDM Implementation Specialist} \\
Facilitated system design and implementation of the Sun Java Identity stack for large client deployments.}
%------------------------------------------------
\entry
{2002-2007}
{DIEBOLD ELECTION SYSTEMS}
{Vancouver, British Columbia}
{\emph{Senior Systems Administrator} \\
Responsible for companywide infrastructure, planning and implementing growth. Supported business with numerous integrated solutions.}
%------------------------------------------------
\entry
{2001-2002}
{SYNTECOR LTD.}
{Vancouver, British Columbia}
{\emph{Java Web Developer} \\
Java-based web application programming, using ORDB, EJB / Servlets.}
%------------------------------------------------
\entry
{1999-2001}
{OPENROAD COMMUNICATIONS}
{Vancouver, British Columbia}
{\emph{Web Developer and Systems Administrator} \\
Maintenance and continual improvements to infrastructure. Perl web app development and fax-to-email deployment.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{1997--1999}
{Dipl. T {\normalfont Computer Systems Technology}}
{British Columbia Institute of Technology}
{\emph{Applied Artificial Intelligence} \\ A project utilizing a combined approach of genetic programming and genetic algorithms to derive formulae for the analysis of fractal curves.}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

% \section{awards}

% \begin{entrylist}
%------------------------------------------------
% \entry
% {2011}
% {Postgraduate Scholarship}
% {School of Business, The University of California}
% {Awarded to the top student in their final year of a Bachelors degree.}
%------------------------------------------------
% \end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

% \section{communication skills}

% \begin{entrylist}
%------------------------------------------------
% \entry
% {2011}
% {Oral Presentation}
% {California Business Conference}
% {Presented the research I conducted for my Masters of Commerce degree.}
%------------------------------------------------
% \entry
% {2010}
% {Poster}
% {Annual Business Conference, Oregon}
% {As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}
%------------------------------------------------
% \end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} high availability, automation, root cause analysis, risk analysis, distributed systems \textbf{personal:} scuba diving, bouldering, running, cycling, cinema, photography

%----------------------------------------------------------------------------------------
%	ORGANIZATIONS SECTION
%----------------------------------------------------------------------------------------

\section{organizations}

\textbf{Global Underwater Explorers:} Project management for all Project Baseline marine research programs conducted within British Columbia. Site Manager for reseach program into the wreck of the ex-CCGS Ready.


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}

%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books from the bibliography

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, %heading=subbibliography]
%\end{refsection}

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}